### 2018-03-23 Sections/the_quantum_space_race.tex
Latin quote stubs
Some restructuring and minor changes.
Constellation network

Currently there are only two satellites with the capability of sending and/or receiving photons through space: the Chinese QUESS\index{QUESS}, and the Japanese SOCRATES\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)} satellites. In order to achieve world-wide coverage multiple satellites will be necessary such that there be a constellation of satellites that are visible at all times, anywhere on Earth, in a similar manner to the GPS satellite network\index{Global positioning system}.

>>>>

Currently there are only two satellites with the capability of sending and/or receiving photons through space: the Chinese QUESS\index{QUESS}, and the Japanese SOCRATES\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)} satellites. In order to achieve world-wide coverage multiple communicating satellites will be necessary such that there be a constellation of satellites\index{Satellite constellation} that are visible at all times, anywhere on Earth, in a similar manner to the GPS satellite network\index{Global positioning system}, thereby bypassing line-of-sight constraints, as per Fig.~\ref{fig:sat_constellation}.

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{satellite_constellation}
	\caption{A satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time.} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}
